Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2018-11-26 scagnostics.Rmd
just playig with watching tours

The guided tour combines optimisation with interpolation between pairs of planes. Target planes of the path are chosen to maximise the PPI. There are three derivative-free optimisation methods available in the guided tour: \verb# search_better_random# (1), \verb# search_better# (2), and \verb# search_geodesic# (3). Method 1 casts a wide net randomly generating projection planes, computing the PPIs and keeping the best projection. Method 2 conducts a localised maximum search. Method 3 is quite different: a local search is conducted to determine a promising direction, and then this direction is followed until the maximum in that direction is found. In each case, a single target plane is chosen by the search methods, and a tour path generated to interpolate from the current projection to the target plane.

@@

```{r eval=FALSE}
# Quick glimpse of optimisations
quartz()
animate_xy(pipeResc, guided_tour(mineIndex("TIC"), search_f = tourr:::search_better,
                                     cooling=1, alpha = 0.5, max.tries = 5000))
animate_xy(pipeResc, guided_tour(holes, search_f = tourr:::search_better,
                                     cooling=1, alpha = 0.5, max.tries = 5000))
```

>>>>

The guided tour combines optimisation with interpolation between pairs of planes. Target planes of the path are chosen to maximise the PPI. There are three derivative-free optimisation methods available in the guided tour: \verb# search_better_random# (1), \verb# search_better# (2), and \verb# search_geodesic# (3). Method 1 casts a wide net randomly generating projection planes, computing the PPIs and keeping the best projection. Method 2 conducts a localised maximum search. Method 3 is quite different: a local search is conducted to determine a promising direction, and then this direction is followed until the maximum in that direction is found. In each case, a single target plane is chosen by the search methods, and a tour path is generated to interpolate from the current projection to the target plane.

@@

```{r eval=FALSE}
# Quick glimpse of optimisations
myholes <- function(mat) {
    n <- nrow(mat)
    d <- ncol(mat)
    num <- 1 - 1/n * sum(exp(-0.5 * rowSums(mat^2)))
    den <- 1 - exp(-d/2)
    (num/den - 0.7) * 1.43
}
quartz()
set.seed(sample(10000:50000, 1))
animate_xy(pipeResc, guided_tour(scagIndex("Skinny"), search_f = tourr:::search_better, cooling=0.9, alpha = pi, max.tries = 500))
animate_xy(pipeResc, guided_tour(mineIndex("MIC"), search_f = tourr:::search_better, cooling=1, alpha = pi, max.tries = 500))
animate_xy(pipeResc, guided_tour(mineIndex("TIC"), search_f = tourr:::search_better, cooling=1, alpha = pi, max.tries = 5000))
animate_xy(pipeResc, guided_tour(holes, search_f = tourr:::search_geodesic,
      cooling=0.8, alpha = pi, max.tries = 500))
```
